---
title: "EML Grid-world analyses"
author: "Andrew Lampinen"
output: html_document
---

```{r}
library(tidyverse)
library(lme4)
library(lmerTest)
#library(stargazer)
```

```{r}
theme_set(theme_classic())
```

```{r}

results_dir = "../results/grids_final/"

language_homm_results_subdirs = c("../language_HoMM_results/language_HoMM_refixed") # fixed two bugs in language HoMM x RL
#language_homm_results_subdirs = c("lessplit_wn_one_holdout/language_HoMM")

language_results_subdirs = c("lessplit_wn_one_holdout/language")
library_results_subdirs = c("lessplit_one_holdout", "lessplit_wn_one_holdout", "lessplit_wn_one_holdout_tcnh")
hold_out_regex = "red_blue_True"  # NOTE: we assume hold outs are the same across runs


num_runs = 5
```

# utils and setup
```{r}
read_config = function(config_file) { 
  config = read_delim(config_file, delim="\n") %>%
    separate(`key, value`, c("key", "value"), sep=",", extra="merge") %>%
    spread(key, value) %>%
    mutate_at(c("games", "hold_outs", "meta_tasks"), function(x) {
      x = gsub("\\\"|[][]| |\'", "", x)
      return(str_split(x, ","))
    } )
}
```

```{r}
load_d = function(results_dir, result_subdirs, num_runs, with_library, file_type) {
  d = data.frame()
  if (num_runs == F) {
    num_runs = 1
    single_runs = TRUE
  } else{
    single_runs = F
  }
  for (run_i in 0:(num_runs-1)) {
    for (result_subdir in result_subdirs) {
      if (single_runs) {
        filename = sprintf("%s%s/%s.csv", results_dir, result_subdir, file_type)
      } else {
        if (with_library) {
          filename = sprintf("%s%s/run%i_%s.csv", results_dir, result_subdir, run_i, file_type)
        } else {
          filename = sprintf("%s%s/run_%i_%s.csv", results_dir, result_subdir, run_i, file_type)
        }
      }
      print(filename)
      if (!file.exists(filename)) {
        print(paste("skipping ", filename, sep=""))
        next
      }
      if (file_type == "config") {
        this_d = read_config(filename)
      } else {
        this_d = read.csv(filename, check.names=F, header=T) 
      }
      this_d = this_d %>%
#        mutate(run = 0,
        mutate(run = run_i,
               run_type = result_subdir)
      d = d %>%
        bind_rows(this_d)
    }
    
  }
  return(d)
}
```


# config loading

```{r}
# config_d = load_d(results_dir, result_subdirs, F, F, "config")
# config_d = bind_rows(config_d,
#                      load_d(results_dir, newer_results_subdirs, num_runs, F, "config"))
```

```{r}
# config_d = config_d %>% 
#   rowwise() %>% 
#   mutate(hold_outs = list(sub("sequence_imitation", "sequenceimitation", sub("pick_up", "pickup",hold_outs)))) %>%
#   ungroup() 
```

# base data loading

```{r}
# base_d = load_d(results_dir, result_subdirs, F, F, "base_losses")
# base_d = bind_rows(base_d,
#                    load_d(results_dir, newer_results_subdirs, num_runs, F, "base_losses"))
```

```{r}
lang_d = load_d(results_dir, c(language_results_subdirs, language_homm_results_subdirs), num_runs, T, "language_losses")
```

```{r}
library_base_d = load_d(results_dir, library_results_subdirs, num_runs, T, "losses")
```

```{r}
# base_d = base_d %>%
#   gather(environment_and_metric, value, -epoch, -run_type, -run) %>%
#   mutate(environment_and_metric=sub("pick_up", "pickup", environment_and_metric),
#          environment_and_metric=sub("sequence_imitation", "sequenceimitation", environment_and_metric)) %>%
#   separate(environment_and_metric,
#            c("game_type", "good_color", "bad_color", "switch_colors", "switch_left_right", "metric"),
#            sep="_",
#            extra="merge") %>%
#   spread(metric, value) %>%
#   mutate(environment_name = paste(game_type, good_color, bad_color, switch_colors, switch_left_right, sep="_"))
```

```{r}
lang_d = lang_d %>%
  gather(environment_and_metric, value, -epoch, -run_type, -run) %>%
  mutate(environment_and_metric=sub("pick_up", "pickup", environment_and_metric),
         environment_and_metric=sub("sequence_imitation", "sequenceimitation", environment_and_metric)) %>%
  separate(environment_and_metric,
           c("game_type", "good_color", "bad_color", "switch_colors", "switch_left_right", "metric"),
           sep="_",
           extra="merge") %>%
  spread(metric, value) %>%
  mutate(environment_name = paste(game_type, good_color, bad_color, switch_colors, switch_left_right, sep="_"))
```

```{r}
library_meta_loss_d = library_base_d %>%
  rename(switch_colors_mapping_loss=`switch_colors:train`) %>%
  select(run, run_type, epoch, switch_colors_mapping_loss)
  

library_base_d = library_base_d %>%
  select(-starts_with("switch_colors")) %>%
  gather(environment_and_metric, value, -epoch, -run_type, -run) %>%
  mutate(environment_and_metric=sub("pick_up", "pickup", environment_and_metric),
         environment_and_metric=sub("sequence_imitation", "sequenceimitation", environment_and_metric)) %>%
  separate(environment_and_metric, 
           c("game_type", "good_color", "bad_color", "switch_colors", "switch_left_right", "metric"),
           sep="_",
           extra="merge") %>%
  spread(metric, value) %>%
  mutate(environment_name = paste(game_type, good_color, bad_color, switch_colors, switch_left_right, sep="_"))
```

```{r}
# check_if_eval = function(environment_name, this_run_type) {
#   these_hold_outs = config_d %>% 
#     filter(run_type == this_run_type) %>% 
#     pull(hold_outs) %>%
#     unlist()
#   return(environment_name %in% these_hold_outs)
# }

check_if_eval = function(environment_name){
  grepl(hold_out_regex, environment_name) 
}
```

```{r}
# base_d = base_d %>% 
#   mutate(eval = grepl(hold_out_regex, environment_name))
```

```{r}
lang_d = lang_d %>% 
  mutate(eval = grepl(hold_out_regex, environment_name))
```

```{r}
library_base_d = library_base_d %>% 
  mutate(eval = grepl(hold_out_regex, environment_name))
```

# basic plot

```{r}
# ggplot(base_d,
#        aes(x=epoch, y=returns_mean, color=game_type, linetype=eval)) +
#   geom_line(stat="summary",
#             fun.y="mean") +
#   geom_hline(yintercept=0,
#              linetype=2) +
#   facet_wrap(~ run_type, scales = "free")
```

```{r}
# ggplot(base_d,
#        aes(x=epoch, y=returns_mean, color=game_type, linetype=eval)) +
#   geom_line(stat="summary",
#             fun.y="mean") +
#   geom_hline(yintercept=0,
#              linetype=2)+
#   geom_hline(yintercept=4,
#              linetype=3) +
#   labs(y="Meta-learning average return") +
#   facet_grid(run_type~run)
# #ggsave("plots/basic_meta_learning.png")
```

```{r}
ggplot(library_base_d,
       aes(x=epoch, y=mean_rewards, color=game_type, linetype=eval)) +
  geom_line(stat="summary",
            fun.y="mean") +
  geom_hline(yintercept=0,
             linetype=2)+ 
  geom_hline(yintercept=4,
             linetype=3) +
  labs(y="Meta-learning average return") +
  facet_grid(run~run_type)
#ggsave("plots/basic_meta_learning.png")
```

```{r}
# ggplot(base_d %>% 
#          filter(game_type == "shooter"),
#        aes(x=epoch, y=returns_mean, linetype=eval)) +
#   geom_line(stat="summary",
#             fun.y="mean") +
#   facet_wrap(~ run_type, scales = "free")
```

```{r}
# ggplot(base_d,
#        aes(x=epoch, y=steps_mean, color=game_type, linetype=eval)) +
#   geom_line(stat="summary",
#             fun.y="mean") +
#   facet_wrap(~ run_type, scales = "free")
```

# meta data loading

```{r}
# meta_d = load_d(results_dir, result_subdirs, F, F, "meta_true_losses")
# meta_d = bind_rows(meta_d,
#                    load_d(results_dir, newer_results_subdirs, num_runs, F, "meta_true_losses"))
```

```{r}
library_meta_d = load_d(results_dir, library_results_subdirs, num_runs, T, "meta_true_losses")
```

```{r}
lang_meta_d = load_d(results_dir, language_homm_results_subdirs, num_runs, T, "language_meta_true_losses")
```

```{r}
# meta_d = meta_d %>%
#   gather(meta_data_point, value, -epoch, -run_type, -run) %>%
#   separate(meta_data_point,
#            c("meta_task", "source", "target_and_metric"),
#            sep=":|->",
#            extra="merge") %>%
#   mutate(metric = str_extract(target_and_metric, "(steps|returns)_(mean|se)$"),
#          target = sub("(steps|returns)_(mean|se)$", "", target_and_metric)) %>%
#   spread(metric, value) %>%
#   mutate(eval = grepl("\\[eval\\]", meta_task),
#          meta_task = sub("\\[eval\\]", "", meta_task),
#          source_is_eval = check_if_eval(source)) %>%
#   mutate(source=sub("pick_up", "pickup", source),
#          source=sub("sequence_imitation", "sequenceimitation", source)) %>%
#   separate(source,
#            c("source_game_type", "source_good_color", "source_bad_color", "source_switch_colors", "source_switch_left_right"),
#            sep="_",
#            extra="merge")
```

```{r}
library_meta_d = library_meta_d %>%
  left_join(library_meta_loss_d) %>%
  gather(meta_data_point, value, -epoch, -run_type, -run, -switch_colors_mapping_loss) %>%
  separate(meta_data_point, 
           c("meta_task", "meta_mapping_toe", "base_task_toe", "source", "target"),
           sep=":|->",
           extra="merge") %>%
  mutate(eval = grepl("\\[eval\\]", meta_task),
         meta_task = sub("\\[eval\\]", "", meta_task),
         source_is_eval = check_if_eval(source)) %>%
  mutate(source=sub("pick_up", "pickup", source),
         source=sub("sequence_imitation", "sequenceimitation", source)) %>%
  separate(source, 
           c("source_game_type", "source_good_color", "source_bad_color", "source_switch_colors", "source_switch_left_right"),
           sep="_",
           extra="merge")
```

```{r}
lang_meta_d = lang_meta_d %>%
  gather(meta_data_point, value, -epoch, -run_type, -run) %>%
  separate(meta_data_point, 
           c("meta_task", "meta_mapping_toe", "base_task_toe", "source", "target"),
           sep=":|->",
           extra="merge") %>%
  mutate(eval = grepl("\\[eval\\]", meta_task),
         meta_task = sub("\\[eval\\]", "", meta_task)) %>%
  mutate(source=sub("pick_up", "pickup", source),
         source=sub("sequence_imitation", "sequenceimitation", source)) %>%
  separate(source, 
           c("source_game_type", "source_good_color", "source_bad_color", "source_switch_colors", "source_switch_left_right"),
           sep="_",
           extra="merge")
```


```{r}
ggplot(lang_meta_d %>%
         filter(meta_task == "switch_colors"),
       aes(x=epoch, y=value, color=source_game_type, linetype=base_task_toe)) +
  geom_line(stat="summary",
            fun.y="mean") +
  geom_hline(yintercept=0,
             linetype=2) +
  facet_grid(run ~ run_type, scales="free")
```

# basic plot

```{r}
ggplot(library_meta_d %>%
         filter(meta_task == "switch_colors"),
       aes(x=epoch, y=value, color=source_game_type, linetype=base_task_toe)) +
  geom_line(stat="summary",
            fun.y="mean") +
  geom_hline(yintercept=0,
             linetype=2) +
  facet_grid(run ~ run_type, scales="free")
```

```{r}
ggplot(library_meta_d %>%
         filter(meta_task == "switch_colors",
                epoch > 20000,
                base_task_toe == "example_is_eval",
                run_type == "lessplit_wn_one_holdout"),
       aes(x=log(switch_colors_mapping_loss), y=value, color=source_game_type)) +
  geom_point() +
  geom_hline(yintercept=0,
             linetype=2) +
  facet_grid(run ~ run_type, scales="free")
```

```{r}
ggplot(library_meta_d %>%
         filter(meta_task == "switch_colors",
                epoch > 20000,
                run_type == "lessplit_wn_one_holdout") %>%
         group_by(base_task_toe, run, epoch) %>%
         summarize(mean_reward = mean(value), switch_colors_mapping_loss=head(switch_colors_mapping_loss, 1)) %>%
         spread(base_task_toe, mean_reward),
       aes(x=log(example_is_train) - log(switch_colors_mapping_loss), y=example_is_eval)) +
  geom_point() +
  geom_hline(yintercept=0,
             linetype=2) +
  facet_wrap(~ run, scales="free")
```

```{r}
criterion=3.8
ggplot(library_meta_d %>%
         filter(meta_task == "switch_colors",
                epoch > 20000,
                run_type == "lessplit_wn_one_holdout") %>%
         group_by(source_game_type, base_task_toe, run, epoch) %>%
         summarize(mean_reward = mean(value), switch_colors_mapping_loss=head(switch_colors_mapping_loss, 1)) %>%
         unite("game_and_toe", source_game_type, base_task_toe, sep=":") %>%
         spread(game_and_toe, mean_reward) %>%
         mutate(above_criterion = `pusher:example_is_train` > criterion & `pickup:example_is_train` > criterion) %>%
         filter(above_criterion) %>%
         select(-contains("example_is_train")) %>%
         gather(game_and_toe, mean_reward, contains("example_is_eval")) %>%
         separate(game_and_toe, c("source_game_type", "base_task_toe"), sep=":"),
       aes(x=log(switch_colors_mapping_loss), y=mean_reward, color=source_game_type)) +
  geom_point() +
  geom_hline(yintercept=0,
             linetype=2) +
  facet_wrap(~ run, scales="free")
```

```{r}
criterion=3.8
ggplot(library_meta_d %>%
         filter(meta_task == "switch_colors",
                epoch > 50000,
                run_type == "lessplit_wn_one_holdout") %>%
         group_by(source_game_type, base_task_toe, run, epoch) %>%
         summarize(mean_reward = mean(value), switch_colors_mapping_loss=head(switch_colors_mapping_loss, 1)) %>%
         unite("game_and_toe", source_game_type, base_task_toe, sep=":") %>%
         spread(game_and_toe, mean_reward) %>%
         mutate(above_criterion = `pusher:example_is_train` > criterion & `pickup:example_is_train` > criterion) %>%
         filter(above_criterion) %>%
         select(-contains("example_is_train")),
       aes(x=`pickup:example_is_eval`, y=`pusher:example_is_eval`, color=log(switch_colors_mapping_loss))) +
  geom_point() +
  geom_hline(yintercept=0,
             linetype=2) +
  facet_wrap(~ run, scales="free")
```
## language homm
```{r}
ggplot(lang_meta_d %>%
         filter(meta_task == "switch_colors"),
       aes(x=epoch, y=value, color=source_game_type, linetype=base_task_toe)) +
  geom_line(stat="summary",
            fun.y="mean") +
  geom_hline(yintercept=0,
             linetype=2) +
  facet_wrap(run ~ run_type, scales="free")
```

# language baselines

```{r}
ggplot(lang_d,
       aes(x=epoch, y=mean_rewards, color=game_type, linetype=eval)) +
  geom_line(stat="summary",
            fun.y="mean") +
  geom_hline(yintercept=0,
             linetype=2) +
  geom_hline(yintercept=4,
             linetype=3) +
  facet_grid(run ~ run_type, scales = "free")
``` 

```{r}
ggplot(lang_d %>%
         filter(run_type == "lessplit_wn_one_holdout/language") %>%
         mutate(eval=factor(eval, labels=c("Trained", "Held-out"))),
       aes(x=epoch, y=mean_rewards/4., color=game_type, linetype=eval)) +
  geom_line(stat="summary",
            fun.y="mean",
            size=1) +
  geom_hline(yintercept=0,
             alpha=0.5,
             linetype=3) +
  geom_hline(yintercept=1,
             alpha=0.5,
             linetype=2) +
  geom_hline(yintercept=-1,
             alpha=0.5,
             linetype=2) +
  scale_y_continuous(breaks = c(-1, -0.5, 0, 0.5, 1), labels = c("-100%", "-50%", "0%", "50%", "100%")) +
  xlim(0, 300000) +
  labs(x="Epoch", y="Normalized returns (evaluation tasks)") +
  scale_color_manual(values=c("#8c510a", "#80cdc1"), breaks=c("pickup", "pusher"), labels=c("Pick-up", "Push-off")) +
  guides(color=guide_legend(title=NULL),
         linetype=guide_legend(title=NULL))

ggsave("../../metamapping_paper/figures/grids_language_learning_curves.pdf", width=4, height=3)
#ggsave("../../../psych/dissertation/4-extending/figures/grids_language_learning_curves.png", width=6, height=4)
``` 


```{r}
ggplot(lang_d %>%
         filter(epoch > 20000),
       aes(x=epoch, y=mean_rewards, color=game_type, linetype=eval)) +
  geom_line(stat="summary",
            fun.y="mean") +
  geom_hline(yintercept=0,
             linetype=2) +
  geom_hline(yintercept=4,
             linetype=3) +
  facet_grid(run ~ run_type, scales = "free")
``` 

Language generalization results are less correlated with train performance and with each-other -- better results with lower criterion.

```{r}
lang_criterion=3.5
ggplot(lang_d %>%
         filter(epoch > 50000,
                run_type == "lessplit_wn_one_holdout/language") %>%
         group_by(run, epoch, game_type, eval) %>%
         summarize(mean_reward = mean(mean_rewards)) %>%
         unite("game_and_toe", game_type, eval, sep=":") %>%
         spread(game_and_toe, mean_reward) %>%
         mutate(above_criterion = `pusher:FALSE` > lang_criterion & `pickup:FALSE` > lang_criterion) %>%
         filter(above_criterion) %>%
         select(-contains("FALSE")),
       aes(x=`pickup:TRUE`, y=`pusher:TRUE`)) +
  geom_point(alpha=0.2) +
  geom_hline(yintercept=0,
             linetype=2) +
  facet_wrap(~ run, scales="free")
```

```{r}
ggplot(lang_d %>%
         filter(epoch < 50000,
                run_type == "lessplit_wn_one_holdout/language") %>%
         group_by(run, epoch, game_type, eval) %>%
         summarize(mean_reward = mean(mean_rewards)) %>%
         unite("game_and_toe", game_type, eval, sep=":") %>%
         spread(game_and_toe, mean_reward) %>%
         # mutate(above_criterion = `pusher:FALSE` > lang_criterion & `pickup:FALSE` > lang_criterion) %>%
         # filter(above_criterion) %>%
         select(-contains("FALSE")),
       aes(x=`pickup:TRUE`, y=`pusher:TRUE`)) +
  geom_point(alpha=0.2) +
  geom_hline(yintercept=0,
             linetype=2) +
  facet_wrap(~ run, scales="free")
```

# comparison

```{r}
criterion=3.8
lang_criterion=3.5
tcnh_criterion=3.5
comparison_d = bind_rows(
  lang_d %>%
    filter(epoch > 50000,
           run_type %in% c("lessplit_wn_one_holdout/language", "../language_HoMM_results/language_HoMM_refixed")) %>%
    group_by(run, run_type, epoch, game_type, eval) %>%
    summarize(mean_reward = mean(mean_rewards)) %>%
    ungroup() %>%
    unite("game_and_toe", game_type, eval, sep=":") %>%
    spread(game_and_toe, mean_reward) %>%
    mutate(above_criterion = `pusher:FALSE` > lang_criterion & `pickup:FALSE` > lang_criterion) %>%
    filter(above_criterion) %>%
    select(-contains("FALSE")) %>%
    mutate(run_type = ifelse(run_type == "lessplit_wn_one_holdout/language", "Language", "LanguageMMLanguageAlone"))  %>%
    rename(pusher=`pusher:TRUE`, pickup=`pickup:TRUE`),
  lang_meta_d %>%
    filter(meta_task == "switch_colors",
           epoch > 50000,
           run_type %in% c("../language_HoMM_results/language_HoMM_refixed")) %>%
    group_by(run_type, source_game_type, base_task_toe, run, epoch) %>%
    summarize(mean_reward = mean(value)) %>%
    ungroup() %>%
    unite("game_and_toe", source_game_type, base_task_toe, sep=":") %>%
    spread(game_and_toe, mean_reward) %>%
    mutate(above_criterion = ifelse(run_type == "lessplit_wn_one_holdout",
                                    `pusher:example_is_train` > criterion & `pickup:example_is_train` > criterion,
                                    `pusher:example_is_train` > tcnh_criterion & `pickup:example_is_train` > tcnh_criterion)) %>%
    filter(above_criterion) %>%
    select(-contains("example_is_train")) %>%
    mutate(run_type = "HoMM\n(from language)") %>%
    rename(pusher=`pusher:example_is_eval`, pickup=`pickup:example_is_eval`),
  library_meta_d %>%
    filter(meta_task == "switch_colors",
           epoch > 50000,
           run_type %in% c("lessplit_wn_one_holdout", "lessplit_wn_one_holdout_tcnh")) %>%
    group_by(run_type, source_game_type, base_task_toe, run, epoch) %>%
    summarize(mean_reward = mean(value), switch_colors_mapping_loss=head(switch_colors_mapping_loss, 1)) %>%
    ungroup() %>%
    unite("game_and_toe", source_game_type, base_task_toe, sep=":") %>%
    spread(game_and_toe, mean_reward) %>%
    mutate(above_criterion = ifelse(run_type == "lessplit_wn_one_holdout",
                                    `pusher:example_is_train` > criterion & `pickup:example_is_train` > criterion,
                                    `pusher:example_is_train` > tcnh_criterion & `pickup:example_is_train` > tcnh_criterion)) %>%
    filter(above_criterion) %>%
    select(-contains("example_is_train"), -switch_colors_mapping_loss) %>%
    mutate(run_type = ifelse(run_type == "lessplit_wn_one_holdout", "HoMM", "HoMM_tcnh")) %>%
    rename(pusher=`pusher:example_is_eval`, pickup=`pickup:example_is_eval`)
) %>%
  select(-above_criterion)
```

Select point to evaluate each task by using the other as a validation task:

```{r}
comparison_d = bind_rows(
  # pickup tasks at max pusher
  comparison_d %>%
    group_by(run_type, run) %>%
    filter(pusher == max(pusher)) %>%
    ungroup() %>%
    select(-pusher) %>%
    mutate(target="pickup", mean_rewards=pickup),
  # pusher tasks at max pickup  
  comparison_d %>%
    group_by(run_type, run) %>%
    filter(pickup == max(pickup)) %>%
    ungroup() %>%
    select(-pickup) %>%
    mutate(target="pusher", mean_rewards=pusher),
)
```

```{r}
comparison_d = comparison_d %>%
  mutate(normalized_rewards = mean_rewards / 4.)
```

## some quick tests

```{r}
perm_mean_diff_test = function(x, y, alpha=0.05) {
  obs_t = t.test(x, y)$statistic
  combined_data = c(x, y)
  n_combined = length(combined_data)
  n_x = length(x)
  perm_iterate = function(x, y) {
    perm = sample(n_combined)
    x_samp = combined_data[perm[1:n_x]]
    y_samp = combined_data[perm[-(1:n_x)]]
    this_t = t.test(x_samp, y_samp)$statistic
    return(this_t)
  }
  perms = replicate(500, perm_iterate(x, y))
  quants = quantile(perms, probs=c(alpha/2, 1-alpha/2))
  return(obs_t < quants[1] | obs_t > quants[2])
}
```

```{r}
set.seed(0)  # reproducibility
perm_mean_diff_test(
  comparison_d %>%
    filter(run_type == "HoMM",
           target == "pickup") %>%
    pull(normalized_rewards),
  comparison_d %>%
    filter(run_type == "Language",
           target == "pickup") %>%
    pull(normalized_rewards)
)
perm_mean_diff_test(
  comparison_d %>%
    filter(run_type == "HoMM",
           target == "pusher") %>%
    pull(normalized_rewards),
  comparison_d %>%
    filter(run_type == "Language",
           target == "pusher") %>%
    pull(normalized_rewards)
)
```

```{r}
lmer(normalized_rewards ~ run_type + target + (1|run),
     comparison_d %>%
       filter(run_type %in% c("HoMM", "Language"))) %>%
  summary()
```

```{r}
lmer(normalized_rewards ~ run_type * target + (1|run),
     comparison_d %>%
       filter(run_type != "HoMM_tcnh")) %>%
  summary()
```

```{r}
lmer(normalized_rewards ~ run_type * target + (1|run),
     comparison_d %>%
       filter(run_type %in% c("HoMM", "HoMM\n(from language)"))) %>%
  summary()
```

## and a plot


```{r}
g = ggplot(data=comparison_d %>%
         filter(run_type %in% c("HoMM", "HoMM\n(from language)", "Language")) %>%
         mutate(run_type=factor(run_type, 
                                levels=c("HoMM", "HoMM\n(from language)", "Language"),
                                labels=c("MM\n(ex.)", "MM\n(lang.)", "Lang.\nAlone"))),
       aes(x=target, 
           color=run_type,
           y=normalized_rewards)) +
  geom_hline(yintercept=1, linetype=2, alpha=0.5) +
  geom_hline(yintercept=0., linetype=3, alpha=0.5) +
  geom_hline(yintercept=-1, linetype=2, alpha=0.5) +
  geom_errorbar(stat="summary",
                fun.data="mean_cl_boot",
                width=0.75,
                size=1,
                position=position_dodge(0.75)) +
  geom_point(stat="summary",
             fun.y="mean",
             size=3,
             position=position_dodge(0.75)) +
  #scale_color_manual(values=c("#e41a1c", "#fec44f", "#02205b")) +
  scale_color_manual(values=c("#f55784", "#7e0146", "#158035")) +
  labs(x="Task", y="Normalized returns (evaluation tasks)") +
  annotate("text", x=0.68, y=0.1, alpha=0.5, label="Chance") +
  annotate("text", x=1.03, y=1.1, alpha=0.5, label="Optimal adaptation") +
  annotate("text", x=0.88, y=-1.1, alpha=0.5, label="No adaptation") +
  scale_y_continuous(breaks = c(-1, -0.5, 0, 0.5, 1), labels = c("-100%", "-50%", "0%", "50%", "100%")) +
  scale_x_discrete(breaks=c("pickup", "pusher"), labels=c("Pick-up", "Push-off")#, expand=expansion(add=c(0.8, 1.2))
                   )

#g +
#  guides(color=guide_legend(title=NULL)) #+
#  #theme(legend.position=c(0.85, 0.75)) 
#ggsave("../../../psych/dissertation/4-extending/figures/grids_adaptation_results.png", width=6, height=4)

g +
  guides(color=guide_legend(title=NULL)) +
  theme(#legend.position=c(0.9, 0.515),
        legend.key.height=unit(0.8, "cm"),
        #legend.background=element_blank(),
        legend.box.margin=margin(0, 0, 0, 0),
        legend.box.spacing=unit(0, 'lines'),
        legend.box.background=element_blank()) 
ggsave("../../metamapping_paper/figures/grids_adaptation_revised_color_test.png", width=4, height=3)
ggsave("../../metamapping_paper/figures/grids_adaptation_revised.pdf", width=4, height=3)

```

```{r}
set.seed(0) # reproducibility
comparison_d %>%
  group_by(run_type, target) %>%
  do(results1=mean_cl_boot(.$normalized_rewards)) %>%
  mutate(performance=results1$y,
         performance95min=results1$ymin,
         performance95max=results1$ymax,
            )
```

```{r}
lmer(normalized_rewards ~ run_type + target + (1|run),
     data=comparison_d) %>%
  summary()
```


## Performance more correlated with MM

```{r}

for (this_lang_criterion in c("strict", "loose")) {
  if (this_lang_criterion == "strict") {
    this_lang_criterion_val = criterion  # as used for HoMM in eval selection above
  } else {
    this_lang_criterion_val = lang_criterion  # as used for language
  }
  perf_corr_d = bind_rows(
    lang_d %>%
      filter(epoch > 50000,
             run_type == "lessplit_wn_one_holdout/language") %>%
      group_by(run, epoch, game_type, eval) %>%
      summarize(mean_reward = mean(mean_rewards)) %>%
      unite("game_and_toe", game_type, eval, sep=":") %>%
      spread(game_and_toe, mean_reward) %>%
      mutate(above_criterion = `pusher:FALSE` > lang_criterion & `pickup:FALSE` > lang_criterion) %>%
      filter(above_criterion) %>%
      select(-contains("FALSE")) %>%
      rename(pusher=`pusher:TRUE`,
             pickup=`pickup:TRUE`) %>%
      mutate(run_type = "Language"),
  library_meta_d %>%
    filter(meta_task == "switch_colors",
           epoch > 50000,
           run_type == "lessplit_wn_one_holdout") %>%
    group_by(source_game_type, base_task_toe, run, epoch) %>%
    summarize(mean_reward = mean(value)) %>%
    unite("game_and_toe", source_game_type, base_task_toe, sep=":") %>%
    spread(game_and_toe, mean_reward) %>%
    mutate(above_criterion = `pusher:example_is_train` > criterion & `pickup:example_is_train` > criterion) %>%
    filter(above_criterion) %>%
    select(-contains("example_is_train")) %>%
    rename(pickup=`pickup:example_is_eval`,
           pusher=`pusher:example_is_eval`) %>%
    mutate(run_type = "MM\n(ex.)")
  ) %>%
    mutate(run_type = factor(run_type, levels=c("MM\n(ex.)", "Language")))
  
  ggplot(perf_corr_d,
         aes(x=pickup/4., y=pusher/4., color=run_type)) +
    geom_hline(yintercept=0,
               alpha=0.5,
               linetype=3) +
    geom_hline(yintercept=1.,
               alpha=0.5,
               linetype=2) +
    geom_hline(yintercept=-1.,
               alpha=0.5,
               linetype=2) +
    #scale_color_manual(values=c("#e41a1c", "#477ec8")) +
    scale_color_manual(values=c("#f55784", "#158035")) +
    # stat_smooth(aes(group=interaction(run_type, run)),
    #             geom='line',
    #             alpha=0.5,
    #             se=F,
    #             method="lm") +
    geom_point() +
    geom_smooth(method="lm") +
    scale_x_continuous(breaks = c(-1, -0.5, 0, 0.5, 1), labels = c("-100%", "-50%", "0%", "50%", "100%")) +
    scale_y_continuous(breaks = c(-1, -0.5, 0, 0.5, 1), labels = c("-100%", "-50%", "0%", "50%", "100%")) +
    labs(x="Normalized returns on pick-up eval.", y="Normalized returns on push-off eval.") +
    guides(color=guide_legend(title=NULL, override.aes=list(fill="#ffffff"))) +
    #guides(color=guide_legend(title=NULL)) +
    theme(legend.position=c(0.85, 0.25)) 
  ggsave(sprintf("../../metamapping_paper/figures/grids_adaptation_correlation_%s.pdf", this_lang_criterion), width=4, height=3)
  #ggsave(sprintf("../../../psych/dissertation/4-extending/figures/grids_adaptation_correlation_%s.png", this_lang_criterion), width=6, height=4)
}
```

```{r}
ggplot(perf_corr_d,
       aes(x=pickup/4., y=pusher/4., color=run_type)) +
  geom_hline(yintercept=0,
             alpha=0.5,
             linetype=3) +
  geom_hline(yintercept=1.,
             alpha=0.5,
             linetype=2) +
  geom_hline(yintercept=-1.,
             alpha=0.5,
             linetype=2) +
  #scale_color_manual(values=c("#e41a1c", "#02205b")) +
  scale_color_manual(values=c("#f55784", "#158035")) +
  #scale_color_manual(values=c("#e41a1c", "#477ec8")) +
  # stat_smooth(aes(group=interaction(run_type, run)),
  #             geom='line',
  #             alpha=0.5,
  #             se=F,
  #             method="lm") +
  geom_point() +
  geom_smooth(method="lm") +
  scale_x_continuous(breaks = c(-1, -0.5, 0, 0.5, 1), labels = c("-100%", "-50%", "0%", "50%", "100%")) +
  scale_y_continuous(breaks = c(-1, -0.5, 0, 0.5, 1), labels = c("-100%", "-50%", "0%", "50%", "100%")) +
  labs(x="Normalized returns on pick-up evaluation", y="Normalized returns on push-off evaluation") +
  facet_wrap(~ run) +
  guides(color=guide_legend(title=NULL, override.aes=list(fill="#ffffff"))) +
  theme(legend.position=c(0.85, 0.25)) 
ggsave("../../metamapping_paper/figures/grids_adaptation_correlation_loose_by_run.pdf", width=8, height=5)
#ggsave("../../../psych/dissertation/4-extending/figures/grids_adaptation_correlation_loose_by_run.png", width=8, height=5)
```
### statistics

```{r}
lmer(pusher ~ pickup * run_type + scale(epoch) + (1 + pickup |run),
     data=perf_corr_d %>%
       mutate(run_type = factor(run_type, 
                                levels=c("Language", "MM\n(ex.)")))) %>%
  summary()
```

```{r}
cor.test(~ pusher + pickup,
         perf_corr_d %>%
           filter(run_type == "Language"))
cor.test(~ pusher + pickup,
         perf_corr_d %>%
           filter(run_type == "MM\n(ex.)"))
```

# tcnh comparison


```{r}
ggplot(data=comparison_d %>%
         filter(run_type %in% c("HoMM", "HoMM_tcnh")) %>%
         mutate(run_type=factor(run_type, 
                                levels=c("HoMM", "HoMM_tcnh"),
                                labels=c("HyperNetwork\narchitecture",
                                         "Task concatenated\narchitecture"))),
       aes(x=target, 
           color=run_type,
           y=normalized_rewards)) +
  geom_hline(yintercept=1, linetype=2, alpha=0.5) +
  geom_hline(yintercept=0., linetype=3, alpha=0.5) +
  geom_hline(yintercept=-1, linetype=2, alpha=0.5) +
  geom_errorbar(stat="summary",
                fun.data="mean_cl_boot",
                width=0.5,
                size=1,
                position=position_dodge(0.5)) +
  geom_point(stat="summary",
             fun.y="mean",
             size=4,
             position=position_dodge(0.5)) +
  scale_color_manual(values=c("#e41a1c", "#841010")) +
  labs(x="Task", y="Normalized returns (evaluation tasks)") +
  annotate("text", x=0.6, y=0.1, alpha=0.5, label="Chance") +
  annotate("text", x=0.86, y=1.1, alpha=0.5, label="Optimal adaptation") +
  annotate("text", x=0.75, y=-1.1, alpha=0.5, label="No adaptation") +
  scale_y_continuous(breaks = c(-1, -0.5, 0, 0.5, 1), labels = c("-100%", "-50%", "0%", "50%", "100%")) +
  scale_x_discrete(breaks=c("pickup", "pusher"), labels=c("Pick-up", "Push-off")) +
  guides(color=guide_legend(title=NULL)) +
  theme(legend.position=c(0.8, 0.25)) 
ggsave("../../metamapping_paper/figures/grids_hyper_vs_tcnh.pdf", width=4, height=3)
#ggsave("../../../psych/dissertation/4-extending/figures/grids_hyper_vs_tcnh.png", width=6, height=4)
```


# analyses of step counts from restore + record data

```{r}
eval_d = load_d("../results/recordings/", c("final_recordings"), num_runs, T, "eval_stats")
```

```{r}
eval_d = eval_d %>%
  separate(mapping, 
           c("meta_task", "meta_mapping_toe", "base_task_toe", "source", "target"),
           sep=":|->",
           extra="merge") %>%
  mutate(eval = grepl("\\[eval\\]", meta_task),
         meta_task = sub("\\[eval\\]", "", meta_task),
         source_is_eval = check_if_eval(source)) %>%
  mutate(source=sub("pick_up", "pickup", source),
         source=sub("sequence_imitation", "sequenceimitation", source)) %>%
  separate(source, 
           c("source_game_type", "source_good_color", "source_bad_color", "source_switch_colors", "source_switch_left_right"),
           sep="_",
           extra="merge")
```

```{r}
ggplot(data=eval_d %>%
         mutate(base_task_toe=factor(base_task_toe,
                                     levels=c("example_is_train", "example_is_eval"),
                                     labels=c("Trained tasks", "Held-out tasks"))) %>%
         group_by(run, source_game_type, base_task_toe) %>%
         summarize(mean_steps = mean(mean_steps)),
       
       aes(x=source_game_type,
           color=base_task_toe,
           y=mean_steps)) +
  geom_errorbar(stat="summary",
                fun.data="mean_cl_boot",
                width=0.5,
                size=1,
                position=position_dodge(0.5)) +
  geom_point(stat="summary",
             fun.y="mean",
             size=4,
             position=position_dodge(0.5)) +
  scale_color_manual(values=c("#1b7837", "#b295cf")) +
  labs(x="Task", y="Mean steps (meta-mapped)") +
  scale_x_discrete(breaks=c("pickup", "pusher"), labels=c("Pick-up", "Push-off")) +
  scale_y_continuous(breaks=c(25, 50, 75, 100, 125)) +
  guides(color=guide_legend(title=NULL)) +
  theme(legend.position=c(0.25, 0.9)) 
ggsave("../../metamapping_paper/figures/grids_behavioral_uncertainty.pdf", width=4, height=3)
#ggsave("../../../psych/dissertation/4-extending/figures/grids_behavioral_uncertainty.png", width=4, height=3)
```

```{r}
set.seed(0) # reproducibility
eval_d %>%
  group_by(source_game_type, base_task_toe) %>%
  do(results1=mean_cl_boot(.$mean_steps)) %>%
  mutate(performance=results1$y,
         performance95min=results1$ymin,
         performance95max=results1$ymax,
            )
```

```{r}
ggplot(data=eval_d %>%
         gather(metric, value, starts_with("mean")) %>%
         group_by(run, base_task_toe, source_game_type, metric) %>%
         summarize(value = mean(value)) %>%
         ungroup() %>%
         spread(base_task_toe, value) %>%
         mutate(delta=example_is_eval - example_is_train,
                metric=paste(metric, "_delta", sep="")) %>%
         select(-starts_with("example")) %>%
         spread(metric, delta),
       aes(x=mean_reward_delta,
           color=source_game_type,
           y=mean_steps_delta)) +
  geom_point(size=4) +
#  geom_smooth(method="lm", se=F) +
  scale_color_manual(values=c("#8c510a", "#80cdc1"), breaks=c("pickup", "pusher"), labels=c("Pick-up", "Push-off")) +
  labs(x="Mean reward delta (MM train - eval)", y="Mean step delta (MM train - eval)") +
#  scale_x_discrete(breaks=c("pickup", "pusher"), labels=c("Pick-up", "Push-off")) +
  scale_y_continuous(breaks=c(0, 25, 50, 75, 100), limits=c(0, 100)) +
  guides(color=guide_legend(title=NULL)) +
  theme(legend.position=c(0.2, 0.2))
ggsave("../../metamapping_paper/figures/grids_behavioral_uncertainty_by_score_diff.pdf", width=4, height=3)
#ggsave("../../../psych/dissertation/4-extending/figures/grids_behavioral_uncertainty_by_score_diff.png", width=4, height=3)
```